### 2013-09-15 acknowledgements.tex
removed all caps section title

\section*{ACKNOWLEDGEMENTS}
The authors would like to thank Siemens Medical Solution USA, Ultrasound
Division for their in-kind technical support and Ned Danieley for system administration support.
This work was supported by NIH R01CA142824 and the Duke Coulter Translational Grant Program.

>>>>

\section*{Acknowledgements}
The authors would like to thank Siemens Medical Solution USA, Ultrasound
Division for their in-kind technical support and Ned Danieley for computer
system administration support.  This work was supported by NIH R01CA142824 and
the Duke Coulter Translational Grant Program.
